\documentclass{llncs}

\begin{document}

\title{Corpus and evaluation description}
%
\titlerunning{fanghaizhou}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{fanghaizhou}
%
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{}
%
\institute{HIT,\\
\email{fanghaizhou611@163.com},\\
\texttt{}
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
This document is used to describe the specific evaluation principles and data processing of the corpus referenced in the article
\end{abstract}
%
\section{Source of corpus}
The corpus used for annotation comprises the complete WSJ part of the Penn Treebank.
\\
The
\section{Annotation method of corpus}
The context often provides more than one possible antecedent for a VPE: the source clause  doesn’t  always  immediately  precede  the  target  clause  (even  though  this  isusually the case), and the source clause might contain more than one possible VP that can serve as antecedent. In particular, cases of embedded VPs cause potential ambiguities
\section{New annotated evaluation method}
% ---- Bibliography ----
%
\begin{thebibliography}{5}
%
\bibitem {clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and
boundary-value problems for Hamiltonian systems.
Arch. Rat. Mech. Anal. 78, 315--333 (1982)

\bibitem {clar:eke:2}
Clarke, F., Ekeland, I.:
Solutions p\'{e}riodiques, du
p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
Note CRAS Paris 287, 1013--1015 (1978)

\bibitem {mich:tar}
Michalek, R., Tarantello, G.:
Subharmonic solutions with prescribed minimal
period for nonautonomous Hamiltonian systems.
J. Diff. Eq. 72, 28--55 (1988)

\bibitem {tar}
Tarantello, G.:
Subharmonic solutions for Hamiltonian
systems via a $\bbbz_{p}$ pseudoindex theory.
Annali di Matematica Pura (to appear)

\bibitem {rab}
Rabinowitz, P.:
On subharmonic solutions of a Hamiltonian system.
Comm. Pure Appl. Math. 33, 609--633 (1980)

\end{thebibliography}

\end{document}
